INTELLIGENT SYSTEMS

### 2021-04-11 slides/slides_paper6.tex
CMG

\begin{frame}{RELATED WORK}
    The following framework can be used both to perform semantic 
    segmentation and to extract foreground objects. There are various 
    models proposed at the state of the art that carry out a different 
    semantic segmentation and a different foreground segmentation.
    \begin{table}[h!]
        \begin{adjustbox}{max width=\textwidth}
        \begin{tabular}{|p{6cm}|p{6cm}|}
            \hline
            \centering
            \bfseries{Semantic Segmentation Methods} &  ~~~~~~~~~~\bfseries{Foreground Methods} \\
            \hline
            \begin{enumerate}
                \item \emph{Fully Supervised Pixel-Wise Annotation-Based Methods}: trained with 
                pixel-wise labels annotated by people.
                \item \emph{Weakly Supervised Object-level Annotation-Based-Methods}: trained with 
                methods such as object-level annotations based on the use of bounding 
                boxes.
                \item \emph{Weakly Supervised Image-Level Annotation-Based Methods}: trained 
                with image category labels.
            \end{enumerate}
            & 
            \begin{enumerate}
                \item \emph{Joint segmentation-based Methods}: used prior knowledge as supervision.
                \item \emph{Saliency prediction-based Methods}: identify regions present in the human 
                visual scene.
                \item \emph{Object proposal-based Methods}: locate all objects in images.
            \end{enumerate}\\
            \hline
        \end{tabular}
        \end{adjustbox}
    \end{table}
\end{frame}

>>>>

\begin{frame}{RELATED WORK}
    The following framework can be used for both semantic segmentation 
    and foreground object segmentation. There are various models proposed 
    at the state of the art that carry out a different semantic segmentation 
    and a different foreground segmentation.
    \begin{table}[h!]
        \begin{adjustbox}{max width=\textwidth}
        \begin{tabular}{|p{6cm}|p{6cm}|}
            \hline
            \centering
            \bfseries{Semantic Segmentation Methods} &  ~\bfseries{Foreground Segmentation Methods} \\
            \hline
            \begin{enumerate}
                \item \emph{Fully Supervised Pixel-Wise Annotation-Based Methods}: trained with 
                pixel-wise labels annotated by people.
                \item \emph{Weakly Supervised Object-level Annotation-Based-Methods}: trained with 
                methods such as object-level annotations based on the use of bounding 
                boxes.
                \item \emph{Weakly Supervised Image-Level Annotation-Based Methods}: trained 
                with image category labels.
            \end{enumerate}
            & 
            \begin{enumerate}
                \item \emph{Joint segmentation-based Methods}: used prior knowledge as supervision.
                \item \emph{Saliency prediction-based Methods}: identify regions present in the human 
                visual scene.
                \item \emph{Object proposal-based Methods}: locate all objects in images.
            \end{enumerate}\\
            \hline
        \end{tabular}
        \end{adjustbox}
    \end{table}
\end{frame}

\begin{frame}{THE PROPOSED APPROACH - 3 Steps}
    The work performed by the model is divided into three steps: \emph{coarse mask generation}, \emph{coarse mask enhancement}, and \emph{recursive mask refinement}.
    \begin{figure}[h!]
        \centering
        \includegraphics[width = 1 \linewidth]{images/paper6/step.png}
        \centering
        \caption{Steps of the proposed method.}
    \end{figure}
\end{frame}

\begin{frame}{THE PROPOSED APPROACH - \emph{Coarse Mask Generation}}
    \begin{minipage}{\linewidth}
        \centering
        \begin{minipage}{0.45\linewidth}
            A CNN network\footnotemark is used to be able 
            to extract a first coarse mask. 
            Unfortunately, as can be seen in 
            the image, the generated masks 
            appear to be inaccurate and do 
            not comply with the position of 
            the underlying object.
        \end{minipage}
        \hspace{0.05\linewidth}
        \begin{minipage}{0.45\linewidth}
            \begin{figure}[h!]
                \centering
                \includegraphics[width = 1 \linewidth]{images/paper6/coarse mask.png}
                \centering
            \end{figure}
        \end{minipage}
    \end{minipage}
    \footnotetext{I. Croitoru, S.-V. Bogolin, and M. Leordeanu, “Unsupervised learning from video to detect foreground objects in single images,” in Proc. IEEE Int. Conf. Comput. Vis. (ICCV), Oct. 2017, pp. 4335–4343.}
\end{frame}
